---
title: "datadict"
output: html_document
---

#Setting Up

```{r}
install.packages("xgboost", repos="https://cran.rstudio.com", lib= "~/")
library(xgboost, lib.loc = "~/")
library(caret, lib.loc = "~/")
library(dplyr, lib.loc = "~/")
```

#Constant variables

```{r}
dat_train <- read.csv("~/santander2/train.csv", stringsAsFactors = FALSE)
dat_test <- read.csv("~/santander2/test.csv", stringsAsFactors = FALSE)

dat_test$TARGET <- NA
all_dat <- rbind(dat_train, dat_test)
count <- 0
for (i in names(all_dat)[-1])
{
	if (is.integer(all_dat[, i]) & length(unique(all_dat[, i])) == 1) 
	{
			all_dat[, i] <- NULL
			cat("Deleted constant variable: ", i, "\n")
		  count <- count + 1
	}
}

cat("Deleted ", count, " constant variables.")
```

#Duplicate columns

```{r}
temp <- names(all_dat)[duplicated(lapply(all_dat, summary))]
cat(temp, sep="\n")
all_dat <- all_dat[!duplicated(lapply(all_dat, summary))]
cat("Deleted ", length(temp), " duplicated variables.")
```

#Correlated variables

Note: this prevents overfitting

```{r}
cor_v <- abs(cor(all_dat))
diag(cor_v) <- 0
cor_v[upper.tri(cor_v)] <- 0
cor_v <- as.data.frame(which(cor_v > 0.85, arr.ind = T))
cat(names(all_dat)[unique(cor_v$row)], sep="\n")
all_dat <- all_dat[,-unique(cor_v$row)]
cat("Deleted ", length(unique(cor_v$row)), " correlated variables.")
```

#Importance

```
xgbmodel <- xgboost(data=dtrain, nrounds=500, max.depth=5, eta=0.01, maximize=T, params=param)
Dimnames <- names(select(train, -ID, -TARGET))
importance_matrix <- xgb.importance(Dimnames,model= xgbmodel)
xgb.plot.importance(importance_matrix)
```

#Variables with missing values

```{r}
summary(all_dat$var3)
summary(all_dat[,grep('delta', names(all_dat))])
```


#Variables included in the model

```{r}
names(all_dat)
```

#Variables that are categorical

```{r}
num_vars <- names(all_dat)[ grep('^num_var', names(all_dat))]
num_vars

for(i in num_vars){
  temp <- aggregate(formula(paste0("TARGET ~ ", i)), data=all_dat, FUN=mean)
  colnames(temp) <- c(i, paste0(i, "_kevin"))
  temp[temp[, 2] == -1, 2] <- NA 
  all_dat <- merge(all_dat, temp, by=i)
}
```

#Tuning

Stepsize (eta) = 0.01 seems to be the best.

max.depth = 5 seems to be the best.

#Variables Recognition
AGE = var15

#New
var42 num
num_ are ranges??

var17 financing product?