---
title: "Personal Notes"
output: html_document
---

#Setting Up

```{r}
library(xgboost)
library(caret)
library(dplyr)
```

#Constant variables

```{r}
dat_train <- read.csv("train.csv", stringsAsFactors = FALSE)
dat_test <- read.csv("test.csv", stringsAsFactors = FALSE)

dat_test$TARGET <- -1
all_dat <- rbind(dat_train, dat_test)
count <- 0
for (i in names(all_dat)[-1])
{
	if (is.integer(all_dat[, i]) & length(unique(all_dat[, i])) == 1) 
	{
			all_dat[, i] <- NULL
			cat("Deleted constant variable: ", i, "\n")
		  count <- count + 1
	}
}

cat("Deleted ", count, " constant variables.")
```

#Duplicate columns

```{r}
temp <- names(all_dat)[duplicated(lapply(all_dat, summary))]
cat(temp, sep="\n")
all_dat <- all_dat[!duplicated(lapply(all_dat, summary))]
cat("Deleted ", length(temp), " duplicated variables.")
```

#Correlated variables

Note: this prevents overfitting

```{r}
cor_v <- abs(cor(all_dat))
diag(cor_v) <- 0
cor_v[upper.tri(cor_v)] <- 0
cor_v <- as.data.frame(which(cor_v > 0.85, arr.ind = T))
cat(names(all_dat)[unique(cor_v$row)], sep="\n")
all_dat <- all_dat[,-unique(cor_v$row)]
cat("Deleted ", length(unique(cor_v$row)), " correlated variables.")
```


#Variables with missing values

```{r}
boxplot(all_dat$var3)
boxplot(all_dat[,grep('delta', names(all_dat))])
boxplot(all_dat$var36)
```

# multi-class variables

```{r}
barplot(table(all_dat$var36))
```

# binary variables
```{r}
for(i in grep('^ind_', names(all_dat)) ){
    print(table(all_dat[, i]))
}

```

#Variables included in the model

```{r}
all_dat <- rename(all_dat, age=var15)
names(all_dat)

train <- all_dat[all_dat$ID %in% dat_train$ID, ]

test <- all_dat[all_dat$ID %in% dat_test$ID, ]

```


#Importance

```{r}
param <- list(objective = "binary:logistic",
              booster = "gbtree",
			  eval_metric = "auc",
              nthread=2,
			  eta=0.02,
			  max_depth=5,
			  colsample_bytree=0.7,
			  subsample=0.7)

xgbmodel <- xgboost(data=as.matrix(train[, !names(train) %in% c("ID", "TARGET")]),
                    label=train$TARGET,
                    nrounds=300, maximize=T, params=param,
                    missing=NA, verbose=0)
Dimnames <- names(select(train, -ID, -TARGET))
importance_matrix <- xgb.importance(Dimnames,model= xgbmodel)

importance_matrix
```

Age is the most important 
```{r}
library(ggplot2)
qplot(age, data=train, colour=as.factor(TARGET), geom='density')
```

saldo_var_30 is also very important

```{r}
qplot(saldo_var30, data=data, color=as.factor(ind_var30), geom='histogram')
qplot(num_var30_0, data=data, color=as.factor(ind_var30_0), geom='histogram')

```

#Tuning

Stepsize (eta) = 0.02 seems to be the best.

max.depth = 5 seems to be the best.

#Variables Recognition
AGE = var15

number of months = '^num_meses*'

#New

var17 financing product?